%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Information Technology Resident} % Job title
    {Google} % Organization
    {Dublin, Ireland} % Location
    {Jul. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide direct and remote support for Linux, OS X, Windows, Chrome OS and Android platforms in addition to network-based applications.}
	\item {Troubleshoot Google's corporate resources and applications. Create and work on bug reports to diagnose and fix long running issues.}
        \item {Develop and participate in local and world-wide IT projects and initiatives, of small to medium complexity.}
        \item {Developed python program to enable fellow technicians to more easily view and understand customer satisfaction feedback left for them. This project saved time for 100+ techs when it came to performance evaluation, allowing them to easily gather metrics in a matter of seconds.}
        \item {Updated internal Chrome extension to view the status of our phone service at a glance. This enabled techs to be able to more easily see if any calls were waiting without needing to be logged into the service.}
        \item {Provide support for services such as video conferencing, remote access and new internal products and mobile technology.}
        \item {Analyze incoming requests and create self-service documentation for Google’s internal users and the global support team. Regularly update articles for our Linux Service Team which require in-depth knowledge of the underlying systems.}
	\item {Work with the Linux Service Team to provide in-depth support for our Linux fleet. This involves handling escalations from other techs which require more in-depth knowledge of our Linux platform to resolve.}
        \item {Work on projects for the Ganeti SRE team in my 20\% time. These projects involved creating a design document and implementing it, usually in Python.}
      \end{cvitems}
    }
 
%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer, Ops Rotation} % Job title
    {Google} % Organization
    {Dublin, Ireland} % Location
    {Jul. 2018 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implement a quarter-long project for a legacy system in Python. This project reduced toil for the team maintaining it and removed blockers on future plans for the legacy system.}
        \item {Troubleshoot bugs in coordination with development teams to resolve a longstanding bug. This resulted in a massive reduction of toil for other teams.}
        \item {Participate in discussions of project and other ongoing discussions with senior SRE team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Workshop Intern} % Job title
    {Qualcom} % Organization
    {Dublin, Ireland} % Location
    {Jun. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Diagnosing and repairing PCs, Printers and Servers}
        \item {Configuring new machines for clients}
        \item {Adding new users in AD and updating emails in Exchange}
        \item {Monitoring tickets through Autotask and resolving them}
        \item {Checking daily backups and collating failed backups into emails for senior staff}
      \end{cvitems}
    }
\end{cventries}

